%------------------------
% Resume
%------------------------

\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]


%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}

  \textbf{{\LARGE Vincenzo Marcella}} \\

  \href
    {https://github.com/vincenzomarcella}{Github: ~~github.com/vincenzomarcella} 
    & Email: 
    \href{mailto:}{me@vincenzomarcella.com} 
  \\

  \href
    {https://www.linkedin.com/in/vincenzomarcella/}
    {LinkedIn: linkedin.com/in/vincenzomarcella/}
    & Mobile:~~~~~~~~+39-388-956-3753  
  \\

  \href
    {https://vincenzomarcella.com}{Website: vincenzomarcella.com}
  \\
  Location: Milan, Italy
\end{tabular*}

%-----------SUMMARY-----------------
\section{Summary}
Cloud Engineer with now 5+ years of experience, with a particular focus on AWS 
Cloud services, and technologies, together with the Serverless Framework. Highly 
proficient in a variety of programming languages, and experienced with multiple 
tools and techniques. Well versed in the entire process that goes from ideation 
to deployment of a product. Specifically skilled in identifying the right 
solution given the request, and delivering a highly efficient, well documented, 
and maintainable deliverable. Very active in the developer community helping to 
organise events and meetups while also actively speaking. Spreading expertise
and knowledge usable to people of all skill ranges. \\
\vspace{-0pt}

%-----------EXPERIENCE-----------------
\section{Experience}
%-----------SERVERLESS GURU------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{Serverless Guru - Serverless Developer} 
    & \textit{January 2023 - Current}
\end{tabular*}

\vspace{-0pt}

Serverless Guru is a US based consulting company, focused on serverless 
technologies. Its aim is to ensure that each and every one of its clients 
can easily and painlessly pivot from legacy technologies to state of the art 
infrastructures, while also revising organisation-level practices and structures 
to maximise results. Furthermore, Serverless Guru is also very active in the 
community by creating courses, content, and various tools; all fully available 
to the serverless community. It boasts a global team, spanning all continents, 
comprised of highly skilled individuals, with the ability to work in 
organisations at all scales, from Fortune 500+ clients to up and coming 
startups. My current role in this company, is to aid clients at all levels, from 
development, to architecture, and organisation while also helping on the 
community side by hosting panels, writing articles and attending events.\par
Tools and technologies used:
\begin{itemize} \vspace{-5pt}
    \item AWS services: Lambda, DynamoDB, S3, Step Functions, SNS, SQS, 
      Eventbridge, Appsync, API Gateway, Cloudfront, IAM, Cognito, 
      Cloudformation, Cloudwatch, X-ray, MSF, Amazon Connect, RDS;
    \vspace{-5pt}
    \item Other tools: Serverless Framework, GitHub Copilot; Amazon Q 
    \vspace{-5pt}
    \item Programming Languages: NodeJS, TypeScript, Python, Apache VTL, Java. 
    \vspace{-5pt}
    
\end{itemize} \vspace{-5pt}
\vspace{5pt}

%-----------AIR CANADA------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{Air Canada - Serverless Developer Consultant 
     (thorugh Serverless Guru)} & \textit{January 2023 - Current}
\end{tabular*}
\vspace{-0pt}
Air Canada is Canada's leading airline. With a multi billion dollar revenue 
stream it is essential to have a solid enterprise IT infrastructure. My current 
role in this company is to design infrastructure, develop, and supervise the 
various teams to ensure that all the best practices are being put in place. A 
special focus has also been put on cost-optimisation, and the maximisation of 
productivity, employing various analysis and AI tools as needed. Furthermore, 
as requested by Air Canada, I've also done various knowledge transfer sessions 
to educate the team in the various possibilities that all sorts of serverless 
tools can open up.\par
Tools and technologies used:
\begin{itemize} \vspace{-5pt}
    \item AWS services: Lambda, DynamoDB, S3, Step Functions, SNS, SQS, 
      Eventbridge, Appsync, API Gateway, Cloudfront, IAM, Cognito, 
      Cloudformation, Cloudwatch, X-ray, MSF, RDS; \vspace{-5pt}
    \item Other tools: Serverless Framework, GitHub Copilot, Amazon Q; 
    \vspace{-5pt}
    \item Programming Languages: Nodejs, Python, Apache VTL, Java. \vspace{-5pt}
    
\end{itemize} \vspace{-5pt}
\vspace{5pt}

%-----------CB DIGITAL COMPANY------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{CB Digital Company(Chiamarsi Bomber) - Back end Tech Lead} & 
    \textit{November 2022 - January 2023}
\end{tabular*}
\vspace{-0pt}
CB Digital Company is the parent company owner of the Chiamarsi Bomber 
multimedia infrastructure. Its main goal is to spread information about the 
sport of football in a relatable and fun manner, aiming to engage all 
demographics with innovative and exciting content. Its latest endeavour being 
the creation of a gamification app, aiming to enhance the user's knowledge of 
the game through the usage of statistics, and trivia. My main goal in this 
experience, was to lead the team in making the correct technical choices, while 
also aiming to modernise the current legacy code. Furthermore, I've also 
predisposed the team for an early and efficient product delivery, by ensuring 
that all the processes and all the best practices were being followed, while 
entering the last part of the development cycle.\par
Tools and technologies used:
\begin{itemize} \vspace{-5pt}
    \item Tools: Serverless Framework, Kubernetes, Docker, MongoDB, \
    Redis; \vspace{-5pt}
    \item Programming Languages: NodeJS, Typescript, Python, Java. \vspace{-5pt}
    
\end{itemize} \vspace{-5pt}
\vspace{5pt}

%-----------SF----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{Starting Finance - Cloud Engineer} & \textit{March 2020 - October 2022}
\end{tabular*}
\vspace{-0pt}
Starting Finance is the point of reference for educational content about finance
for under 30s in Italy. It boasted, at the time, a community of over 400k
members across different platforms nation-wide. Together, we have created a 
mobile app that allows its users to gain exposure to financial products and 
simulate investments on the NYSE and NASDAQ markets with real-time data. The 
core of the app revolves around gamification, and social features, that allow 
the user to compete for prizes based on their wallet's yield, and to interact 
with one another through social features.
I have worked in the team since its inception, always overseeing the development
and engineering; treasuring, and participating in the team's growth by proposing,
and interviewing multiple candidates together with supporting pre-sales and 
marketing tasks. A lot of my work revolved around estimating workloads,
providing different implementation strategies, and cost estimates together with
developing and optimising algorithmic processes. Due to my relative seniority 
in this company, I have first hand experience on the whole product-lifecyclem 
and the bootstrapping of an efficient development team and an effective 
development process.\par
Tools and technologies used:
\begin{itemize} \vspace{-5pt}
    \item AWS services: Lambda, DynamoDB, Timestream, Aurora, S3, 
      Step Functions, SNS, SQS, Eventbridge, Appsync, API Gateway, Amplify,
      Cloudfront, IAM, Cognito, Cloudformation, Cloudwatch, Cloudtrail, X-ray; 
      \vspace{-5pt}
    \item Other tools: Serverless Framework, Lumigo; \vspace{-5pt}
    \item Programming Languages: Nodejs, Golang, Python, Apache VTL. 
    \vspace{-5pt}
    
\end{itemize} \vspace{-5pt}
\vspace{5pt}

%----------ITALIAN ARMY---------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{Italian Army - Full Stack Developer Intern} & \textit{June 2019}
\end{tabular*}
Developed an inventory system to keep track of all the inventory in the training
centre in Aosta, Italy. There we worked closely with the officials managing the 
training centre to develop the most suitable solution given their needs and the 
rather limited time.
Tools and technologies used: MySQL, Nginx, PHP, HTML, CSS, Javascript.
\vspace{-0pt}

%-----------EDUCATION-----------------
\section{Education}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{Bachelor's Degree, Computer Science - University of Milan-Bicocca} 
    & \textit{October 2021 - current} \\
    \textbf{Information Technology Technical High School Diploma - Federico 
    Caffè (Rome)} & \textit{September 2016 - July 2021}
\end{tabular*} 
\vspace{-0pt}

%-----------CERTIFICATIONS-----------------
\section{Certifications}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{Cambridge English - First Certificate in English - Passed with Grade
     A - CEFR Level C1} & \textit{2019} \\
\end{tabular*} 
\vspace{-0pt}


%-----------Skills summary-----------------
\section{Soft skills}
\begin{itemize} 
    \item \textbf{Languages}: Italian(Native), English(Fluent)
    \item \textbf{Leadership and Communication}: Careful listener and observer, 
    always ready to step in when necessary and always available to talk and 
    communicate if a misunderstanding were ever to arise. Also very interested 
    in discussing about productivity and team efficiency. Suited to 
    collaborative environments. \vspace{-5pt}
    \item \textbf{Planning and Organising}: Good time management and resource 
    management, also experienced in planning due to my past and current work 
    environment. Very collaborative and understanding of the team's needs and 
    preferences. Well rounded in Jira and Miro. Also currently one of the 
    organisers of the Serverless Italy group, hosting and presenting at meetups 
    and in the future also at convetions. \vspace{-5pt}
    \item \textbf{Writing}: Very proficient writer of technical documentation 
    and articles, also featured on some articles regarding Serverless computing.
    \vspace{-5pt}
\end{itemize}
\vspace{-0pt}

\end{document}
